Compositional equivalences based on Open pNets

### 2020-04-01 2016-Weak-FH-Bisim/WeakBisim.tex
pages 72-75
ajoute les WI_8 (mais pas verifie par rapport celles de Biyang)
et ajoute les WI_4P, WI_4Q, WI_456*P a la fin...

\begin{figure}[h]
   \centerline{\includegraphics[width=10cm]{XFIG/SimpleProtImpl-WOA}}
  \caption{Weak Open Automaton of the implementation}
   \label{Appendix:ImplOAl}
\end{figure}

In Figure \ref{Appendix:ImplOA} we show the weak open automaton of our implementation pNet. 
\TODO{This version is very uncomplete, at least 12 WOTs are missing, inculding: all variants of WI3 starting from 202; the inverse of WI4, WI5, WI6, WI8, etc}

@@

Figure \ref{Appendix:ImplOA} shows a more compact version of this weak automation, that will be easier to read for humans...
It is based on the observation that states 202 and 000 are only linked by a "pure $\tau$" transition, and have exactly the same possible behaviors.
In this configuration we can garanty that they are Weak Bisimilar, and merge their (incoming and outgoing) transitions in the Figure. We denote this equivalence class of states as $\{000,202\}$.
\TODO{May be express this property more formely, but this could be also part of another paper, more oriented towards algorithms and optimisation of the Weak}

\ERIC{Correspondance between the WOTs naming:
$WI_3 ','',''' -> WI_3 a,b,c$\\
$WI_7 ','' -> WI_7 a,b$\\
$WI_8 ','',''' -> WI_8 a,b,c$\\
$WI_9 ,','' -> W_{456,564,645}$\\
$WI_{4a,5a,6a}$ are new.
}

@@

For all global states $S$:

@@

@@

\medskip
This result is INCORRECT: the Post cannot use $s1\_msg$, this variable is not available in state 220

@@

\TODO{no yet checked (old version), or not yet fully validated ...:}

$Post_{8'''}= post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ Post_{456}^*\shortotimes\ post_{6} = (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+1+n), \forall n\ge 0$

$ WI_{8'''}(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(s1\_msg,s2\_ec}+n)\}, True, ()}
         {210 \OTWeakarrow {\underline{\texttt{out(s1\_msg,s2\_ec+n)}}} 202}
         \ \forall n\ge 1$

$ WI_8(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(r1-msg,r1-ec +n)}\}, True, ()}
         {201 \OTWeakarrow {\underline{\texttt{out(r1-msg,r1-ec +n)}}} 202}
         \ \forall n\ge 0$

$ WI_9(n) = \openrule
         {\{\}, True, (\texttt{m1\_ec}\gets \texttt{m1\_ec}+n)}
         {210 \OTWeakarrow {\tau} 210}
         \ \forall n\ge 0$

>>>>

\begin{figure}[h]
   \centerline{\includegraphics[width=10cm]{XFIG/SimpleProtImpl-WOA}}
  \caption{Weak Open Automaton of the implementation}
   \label{Appendix:ImplOA}
\end{figure}

In Figure \ref{Appendix:ImplOA} we show the weak open automaton of our implementation pNet. 
\TODO{This version is very uncomplete, at least 12 WOTs are missing, including: all variants of WI3 starting from 202; the inverse of WI4, WI5, WI6, WI8, etc}
\TODO{See also the last bunch of ransitions, at the end of the list, for combinations of any $\tau$ transition with an external action of P or Q}

@@

Figure \ref{Appendix:ImplOA2} shows a more compact version of this weak automation, that will be easier to read for humans...
It is based on the observation that states 202 and 000 are only linked by a "pure $\tau$" transition, and have exactly the same possible behaviors.
More tricky, they do not have the same state variables, as 202 has the variables of state $s2$, but none of these variables are used in transitions from 202.
In this configuration we can garantee that they are Weak Bisimilar, and merge their (incoming and outgoing) transitions in the Figure. We denote this 
equivalence class of states as $\{000,202\}$.
\TODO{May be express this property more formely, but this could be also part of another paper, more oriented towards algorithms and optimisation of the Weak}

@@

In the first 3 weak transitions, $S$ denotes the set of all global states.

$ W_\tau = \openrule
{\{\}, True, ()}
{S \OTWeakarrow {\tau} S}$

@@

\medskip
This result ($WI_{6a}$) is INCORRECT: the Post cannot use $s1\_msg$, this variable is not available in state 220

@@

@@

$ WI_8 = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(r1-msg,r1-ec)}\}, True, ()}
         {201 \OTWeakarrow {\underline{\texttt{out(r1-msg,r1-ec)}}} \{202, 000\}}
         \ \forall n\ge 0$

$ WI_{8a}(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(m1\_msg,m1\_ec}+n)\}, True, ()}
         {210 \OTWeakarrow {\underline{\texttt{out(m1\_msg,m1\_ec}+n)}} \{202, 000\}}
         \ \forall n\ge 1$

 $ WI_{8b}(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(??\_msg,s2\_ec}+n)\}, True, ()}
         {220 \OTWeakarrow {\underline{\texttt{out(??\_msg,m2\_ec}+n)}} \{202, 000\}}
         \ \forall n\ge 1$

 $ WI_{8c}(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(s1\_msg,s1\_ec}+n)\}, True, ()}
         {100 \OTWeakarrow {\underline{\texttt{out(s1\_msg,s1\_ec}+n)}} \{202, 000\}}
         \ \forall n\ge 1$

%$Post_{8'''}= post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ Post_{456}^*\shortotimes\ post_{6} = (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+1+n), \forall n\ge 0$

\medskip
Then for all $\tau$ transitions above we have a similar WOT that include a non-$\tau$ move from an external action of P or Q, like for example:

$ WI_4P(n) = \openrule
         {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], 
   (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n, \texttt{s2\_ec}\gets \texttt{s1\_ec}+n)}
         {100 \OTWeakarrow {\texttt{p-a}} 210}
$
and
$ WI_4Q(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{m,ec}. \texttt{q-b} \neq \texttt{q-recv(m,ec)} ],
   (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n, \texttt{s2\_ec}\gets \texttt{s1\_ec}+n)}
         {100 \OTWeakarrow {\texttt{q-b}} 210}
$

but also e.g.:

$ WI_{456*}P(n) = \openrule
        {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], 
    (\texttt{s1\_msg}\gets \texttt{s1\_msg}, \texttt{s1\_ec}\gets \texttt{s1\_ec}+n)}
  {100 \OTWeakarrow {\texttt{p-a}} 100}
        $
